Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue

### 2021-01-15 reports/rmarkdown/manuscript/manuscript_template.Rmd
adds fig2 and figS1-2

  o <- order( rowSums(temp_legend) , decreasing = T)
  sample_o <- order( patient_groups )
  temp <- temp[o,sample_o]*100
  # temp <- temp[-grep("NA",rownames(temp)),]
  temp <- rbind(temp[1:20,], Other = colSums(temp[21:nrow(temp),]) )

>>>>

  o <- order( rowSums(temp_legend) , decreasing = T)
  sample_o <- order( patient_groups )
  temp <- temp[o,sample_o]*100
  # temp <- temp[-grep("NA",rownames(temp)),]
  temp <- rbind(temp[1:16,], Other = colSums(temp[17:nrow(temp),]) )
